Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2018-03-20 paper/presentation/govWebsites_spring_2018_Presentation.tex
presentation

%\begin{frame}{Spot the difference}
%\begin{figure}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{Images/Clinton_Rally_cr.jpg}}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{Images/Trump_Rally_cr.jpg}}
%\end{figure}
%\end{frame}

\begin{frame}{Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
		\item Content of government websites is an important source of information \& transparency
		\item After coming into power, the Trump administration  has made some controversial changes to the websites of federal agencies
		\item Website content is political
		\item Partisanship of city government is expected to have an effect
	\end{itemize}

}
\end{frame}

\begin{frame}{Example Website}
	\includegraphics[width = \linewidth]{arcadia_water.png}
\end{frame}

\begin{frame}{Local Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
		\item Most local (i.e. mayoral) elections are non-partisan
		\item Few states have exclusively partisan local elections
		\item Data for these elections can be difficult to find
		\item We selected Indiana and Louisiana
	\end{itemize}

	}
\end{frame}

\begin{frame}{Data Overview}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
\end{figure}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Identify URLs
		\item Verify URLs (browser automation)
		\item Download websites
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Boilerplate removal
		\item Spellchecking
		\item Lemmatization \\ (city \& cities = city)
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		%\item Hierarchical clustering
		\item Fightin' Words
		\item Structural topic model
		%\begin{itemize}
		%	\item LDA
		%	\item STM
		%\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
	\begin{columns}
		\column{0.33\textwidth}
		%Data Collection
		\vspace{5mm}
		\begin{itemize}
			\item Identify URLs
			\item Verify URLs (browser automation)
			\item Download websites
			\item Determine file type
			\item Convert to txt
		\end{itemize}		
		\column{0.33\textwidth}
		%Preprocessing
		\vspace{5mm}
		\begin{itemize}
			\item Remove punctuation, dates, etc.
			\item To lowercase
			\item \textbf{Boilerplate removal}
			\item Spellchecking
			\item Lemmatization \\ (city \& cities = city)
		\end{itemize}
		\column{0.33\textwidth}
		%Analysis
		\vspace{5mm}
		\begin{itemize}
			%\item Hierarchical clustering
			\item Fightin' Words
			\item Structural topic model
			%\begin{itemize}
			%	\item LDA
			%	\item STM
			%\end{itemize}
		\end{itemize}
	\end{columns}
\end{frame}

\section{Preprocessing}

%\begin{frame}{Document filetype \& conversion}
%\begin{itemize}
%	\item Websites contain a number of different filetypes
%	\item txt, pdf, html, doc and docx are useable
%	\item convert everything to txt
%	\item the file ENDING does not always 
%\end{itemize}
%\end{frame}

\begin{frame}{Boilerplate Removal}
\includegraphics[width = \linewidth]{arcadia_water.png}
\end{frame}

\begin{frame}{Boilerplate Removal}
\includegraphics[width = \linewidth]{duplicateLines.png}
\end{frame}

\begin{frame}{Boilerplate Removal}
	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
\end{frame}

\begin{frame}{Boilerplate Removal}
\begin{itemize}
	\item Within each city, there is a lot of shared text
	\item If not removed, the text clusters into cities
\end{itemize}
\begin{itemize}
	\item Solution: Compare each line in each document to every other line in every document of that city
	\item Count duplicates
	\item Remove a line if it is duplicated within a city above some threshold
	\item Fast \& efficient implementation
\end{itemize}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
	\begin{columns}
		\column{0.33\textwidth}
		%Data Collection
		\vspace{5mm}
		\begin{itemize}
			\item Identify URLs
			\item Verify URLs (browser automation)
			\item Download websites
			\item Determine file type
			\item Convert to txt
		\end{itemize}		
		\column{0.33\textwidth}
		%Preprocessing
		\vspace{5mm}
		\begin{itemize}
			\item Remove punctuation, dates, etc.
			\item To lowercase
			\item Boilerplate removal
			\item Spellchecking
			\item Lemmatization \\ (city \& cities = city)
		\end{itemize}
		\column{0.33\textwidth}
		%Analysis
		\vspace{5mm}
		\begin{itemize}
			%\item Hierarchical clustering
			\item Fightin' Words
			\item Structural topic model
			%\begin{itemize}
			%	\item LDA
			%	\item STM
			%\end{itemize}
		\end{itemize}
	\end{columns}
\end{frame}

%\begin{frame}{Other preprocessing}
%\begin{itemize}
%	\item Remove:
%	\begin{itemize}
%		\item Dates
%		\item Numbers
%		\item Punctuation
%		\item Words not recognized by an English dictionary
%		\item Stopwords
%		\item Documents with too few unique words
%	\end{itemize}
%\item Set to lowercase
%\item Lemmatization
%\end{itemize}
%\end{frame}

\begin{frame}{Data Overview}
\input{descriptiveStatsIN.tex}
\input{descriptiveStatsLA.tex}
\end{frame}

\section{Analysis}
%\begin{frame}{Hierarchical Clustering}
%\centering
%\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
%\end{frame}

%\begin{frame}{Fightin' Words}
%\begin{figure}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
%\end{figure}
%\end{frame}

\begin{frame}{Fightin' Words - Monroe et al. (2008)}
\linespread{1.5}
\begin{itemize}
	\item Goal: Split words based on one binary variable (party)
	\item Find the most Democratic and most Republican words
	\item Problem: Text mostly consists of meaningless words
	\item Solution: Set prior based on expected distribution of words in random text
	\item Method provides a z-Score indicating the degree to which a word is preferred by one party
	\item Very fast to compute
\end{itemize}
\end{frame}

\begin{frame}{Fightin' Words (Indiana)}
	\input{fightinwordsIN.tex}
%	\input{../tables/fightinwordsIN.tex}
\end{frame}

%\begin{frame}{Latent Dirichlet Allocation}
%\input{partisanTopWords.tex}
%\end{frame}

\begin{frame}{Structural Topic Model - Roberts et al. (2014)}
\linespread{1.5}
\begin{itemize}
	\item Topic models find clusters of semantically related words in texts --> i.e. topics
	\item As a clustering method, LDA doesn't explicitly allow for covariates (although post-hoc comparison is possible)
	\item The structural topic model extends this approach to explicitly include (multiple) covariates
	\item Our covariates: Party + City Population
\end{itemize}
\end{frame}

\begin{frame}{Structural Topic Model (Indiana)}
\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

\begin{frame}{Structural Topic Model (Indiana)}
\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
\linespread{1.5}
\large
\begin{itemize}
	%\item Hierarchical clustering only creates 'topics' if content is VERY similar
	%\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
	%\item LDA is sensitive to preprocessing, but the most flexible
	%\item STM works too, but also very sensitive to duplicate content
	\item Manual vs. automatic analysis of government websites
	\item Our pipeline facilities scalable comparative analysis

	\vspace{5mm}
	\item Partisanship affects website content:
	\item Democrats focus on raising and spending money
	\item Republicans focus on infrastructure and utilities
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Presented at SPSA}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Identify URLs
		\item Verify URLs (browser automation)
		\item Download websites
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Boilerplate removal
		\item Spellchecking
		\item Lemmatization \\ (city \& cities = city)
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		%\item Hierarchical clustering
		\item Fightin' Words
		\item Structural topic model
		%\begin{itemize}
		%	\item LDA
		%	\item STM
		%\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{Presented at SPSA}
\input{descriptiveStatsIN.tex}
\input{descriptiveStatsLA.tex}
\end{frame}

\begin{frame}{Presented at SPSA}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
\end{figure}
\end{frame}

\begin{frame}{Presented at SPSA}
	\input{fightinwordsIN.tex}
\end{frame}

\begin{frame}{Presented at SPSA}
\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

\begin{frame}{Presented at SPSA}
\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
\end{frame}

\begin{frame}{SPSA feedback}
\begin{itemize}
	\item overall quite positive
	\item there seems to be some demand in publican administration for this kind of research
	\item threshold of ten for duplicates
	\item the usual concerns with bag-of-words
	\item describe methods more clearly
	\item \textbf{``Does your method improve the external validity so greatly that the internal validity becomes less of a concern?''}
	\item comparison with non-partisan cities/websites
	\item city covariates
\end{itemize}
\end{frame}

\begin{frame}{Planned covariates}
\begin{itemize}
	\item population
	\item GDP per capita
	\item percent non-white
	\item City area
	\item democratic vote share/magnitude of victory
	\item log median house price
	\item (most of these are from Einstein \& Glick 2015)
\end{itemize}
\end{frame}

\begin{frame}{Since SPSA - ground truth test}
\begin{itemize}
	\item party manifestos (didn't work - not enough data)
	\item mayors' campaign websites (LA/IN - didn't work - not much data, and strange results)
	\item mayors' campaign websites (top 100 cities - worked somewhat)
\end{itemize}
{\renewcommand\normalsize{\tiny}%
	\small
	\input{../tables/groundtruth_bootstrapped.tex}}
\end{frame}

\begin{frame}{Since SPSA - extending the sample}
\begin{itemize}
	\item New York
	\item big cities
	\item Washington
	\item Oregon (unsuccessful)
	\item extended LA/IN (55 -> 165)
	\item 314 cities total, 230 downloaded so far
\end{itemize}
\end{frame}

\begin{frame}{wget and www}
\begin{itemize}
	\item www.townoflockport.com/ -- doesn't work
	\item http://townoflockport.com/ -- works
	\item inconsistent across websites
	\item solution: check every website with Selenium, record the url it redirects to
	\item currently re-scraping the 84 websites still missing
\end{itemize}
\end{frame}

\begin{frame}{Next steps: compression}
\begin{itemize}
	\item Since, so far, something has always gone wrong when adjusting file endings and converting files to text, I've always made zipped backups so far
	\item compression of millions of files of more than 1TB
	\begin{itemize}
		\item time
		\item some paths are too long
		\item some filenames have non-ascii characters
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Next steps: map}
\includegraphics[width=\linewidth, height = .99\textheight]{../figures/us_map.pdf}
\end{frame}

\begin{frame}{Next steps: covariates}
\begin{itemize}
	\item I already downloaded the above some time ago, but only for LA and IN
	\item this was already a little convoluted, I'll have to automate it for it to work with all states
	\item there is a problem with the census data:
\end{itemize}
\end{frame}

\begin{frame}{Next steps: covariates}
\begin{itemize}
	\item I already downloaded the above some time ago, but only for LA and IN
	\item this was already a little convoluted, I'll have to automate it for it to work with all states
	\item there is a problem with the census data:
\end{itemize}
\includegraphics[width=\linewidth]{census_problem.png}
\begin{itemize}
	\item Not a priority right now, need to finish all the document-related stuff first
\end{itemize}
\end{frame}

\begin{frame}{Next steps: optimize code}
\begin{itemize}
	\item preprocessing already took 4-5 hours for 25000 documents
	\item we currently have 1.3 million; this will get reduced a bit, but it will still be a huge increase
	\item the functions that aren't already vectorized are currently ``sapply'd''
	\item with this much data, parallelization is probably worth it (currently only hashtables, spellchecking and some other more computationally intensive stuff is parallelized)
	\item MAYBE it would be worth it to translate everything to quanteda - but unfortunately that won't work with the hashtables stuff
	\item fightin' words is pretty fast, but stm also took hours already
\end{itemize}
\end{frame}

\begin{frame}{Next steps: structural topic model}
\begin{itemize}
	\item currently we use separate models for IN, LA
	\item state fixed effects
	\item package has problems with overly complex models
	\item maybe use stm only for IN, LA, NY, WA, CA
\end{itemize}
\end{frame}
